Imposing a Weight Norm Constraint for Neuro-Adaptive Control

### 2025-06-18 presentation/presentation.tex
ppt final peer review 1

% Inbuilt themes in beamer
\documentclass[8pt, aspectratio=169, handout]{beamer}
% \documentclass[8pt, aspectratio=169]{beamer}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Define where theme files are located. ('/styles')
\usepackage{styles/fluxmacros}
\usefolder{styles}
% Use Flux theme v0.1 beta
% Available style: asphalt, blue, red, green, gray 
\usetheme[style=blue]{flux}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro-Adaptive Control 
} 
\subtitle{
    \textit{IEEE European Control Conference (ECC) 2025}\\
}
\author{
  \textbf{Myeongseok Ryu}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
  }
\date{2025-06-25}
\institute{%
    \begin{minipage}[c]{\linewidth}
        \centering
        \inst{1}%
        Department of Mechanical and Robotics Engineering\\
        Gwangju Institute of Science and Technology
        \and
        \inst{2}%
        AI Graduate School\\
        Gwangju Institute of Science and Technology
  \end{minipage}
}
\titlegraphic{assets/MIC_Lab_logo_white.png}
% make institute font size smaller
\setbeamerfont{institute}{size=\normalsize}

@@

  \textbf{Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Neuro-adaptive control} (NAC) is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control} \cite{Farrell:2006aa}.
      \item Features of both \textbf{NNs} and \textbf{adaptive control} can be found in NAC.
    \end{itemize}
  }

@@

  \textbf{Advantages of Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item <+-> \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
      \item <+-> \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textit{Lyapunov stability theory}.
      \item <+-> \textbf{Online Learning Capability}: NAC adapts in \textit{real-time} to new data with stability guarantees.
      \item <+-> \textbf{Robustness}: NAC handles \textit{uncertainties and disturbances} effectively with adaptive control techniques.
    \end{itemize}
  }

@@

\begin{frame}{\insertsubsectionhead}{Existing Challenges in NAC}

  \begin{enumerate}
    \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Weight Boundedness:}

          \begin{itemize}
            \item The NN weights can grow unbounded, leading to instability.
            \item Unbounded weights can cause the NN to produce large control inputs, which may lead to following challenges.
          \end{itemize}

        \column{0.49\textwidth}
          \centering
          \begin{figure}
            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
            \caption{Unbounded NN weights.}
          \end{figure}
      \end{columns}

      \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Unpredictable Amplitude of Control Input:}

          \begin{itemize}
            \item The NN outputs are unpredictable and not interpretable.
            \item This feature and unbounded NN weights can lead to control input saturation.
          \end{itemize}

        \column{0.49\textwidth}
          \centering
          \begin{figure}
            \includegraphics[width=0.8\textwidth]{figures/unpredictable.drawio.pdf}
            \caption{Unpredictable amplitude of NN outputs.}
          \end{figure}
      \end{columns}
  \end{enumerate}

@@

  \begin{enumerate}
    \begin{columns}[T,onlytextwidth]
        \column{0.65\textwidth}
          \item \textbf{Projection Operator} \small{\textit{for weight boundednss}}

          \begin{itemize}
            \item Projects the NN weights onto a convex set.
            \item Ensures that the weights remain within a predefined bound.
          \end{itemize}

          \begin{equation}
            \estwth \leftarrow \myproj_{\overline{\theta}}(\estwth)
          \end{equation}

        \column{0.35\textwidth}
          \begin{figure}
            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
          \end{figure}
      \end{columns}

      \vspace{0.2cm}

      \begin{columns}[T,onlytextwidth]
        \column{0.65\textwidth}
          \item \textbf{$\epsilon$-modification, and $\sigma$-modification} \small{\textit{for weight boundednss}}

          \begin{itemize}
            \item Add a stabilizing term to adaptation law.
            \item Invariance set of the NN weights can be ensured.
          \end{itemize}

          \begin{equation}
            \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \rho \norm{\estwth}
          \end{equation}

        \column{0.35\textwidth}
          \begin{figure}
            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
          \end{figure}

@@

      \vspace{0.2cm}

      \begin{columns}[T,onlytextwidth]
        \column{0.65\textwidth}
          \item \textbf{Additional Control Inputs} \small{\textit{for control saturation}}

          \begin{itemize}
            \item Conventional controllers are used to address control input saturation. 
                  \begin{itemize}
                    \item Barrier Lyapunov function or auxiliary system-based control inputs.
                  \end{itemize}
            \item These methods do not guarantee the stability of the system.     
          \end{itemize}

        \column{0.35\textwidth}

          \begin{figure}
            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
          \end{figure}

      \end{columns}
  \end{enumerate}
\end{frame}

@@

  \textbf{Limitation 1: Lack of Optimality}
  \begin{itemize}
    \item The existing methods do not guarantee the optimality of the control input.
    \item ...
  \end{itemize}

  \textbf{Limitation 2: Disruption of Learning Process by Additional Control Inputs}
  \begin{itemize}
    \item Feedback tracking error for learning is disrupted by additional control inputs.
      \begin{itemize}
        \item The feedback error does not reflect the error induced by the NN, directly.
      \end{itemize}  
    \item 
  \end{itemize}

@@

  \textbf{Contribution 1: Unified Optimization Framework} 
  \begin{itemize}
    \item 
  \end{itemize}

  \textbf{Contribution 2: Online Learning Capability (Stabiltiy Guarantees)}
  \begin{itemize}
    \item 
  \end{itemize}

  \textbf{Contribution 3: Weight and Control Input Constraint Handling}
  \begin{itemize}
    \item 
  \end{itemize}

@@

      \textbf{Target Two-link Robotic Manipulator System}:
      \begin{itemize}
        \item Control input saturation function $\mysat(\cdot)$.
        \item Desired trajectory $\mv{q}_d$ is given.
      \end{itemize}
        \begin{equation}\label{eq:sys}
          \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
          =
          \mysat(\mv{\tau})
        \end{equation}

      \textbf{Control Input}:
      \begin{itemize}
        \item NN's output $\mv{\Phi}$ is used as the control input.
        \item Consists of the estimated NN weights $\estwth$.
      \end{itemize}
      \begin{equation}\label{eq:input}
        \mv{\tau} := \mv{\Phi}(\mv{q}_n; \estwth)
      \end{equation}

      \textbf{Deep Neural Network (DNN)}:
      \begin{itemize}
        \item $k$ layers with $\estwth_i:=\myvec(\estwV_i)$.
        \item Activation function: $\phi(\cdot):=tanh(\cdot)$.
        \begin{equation}\label{eq:NN}
          \mv{\Phi}(\mv{q}_n; \estwth)
          :=
          \begin{cases}
              \estwV_i^\top \act_i(\estNN_{i-1}), 
              &
              i\in\{1,\dots ,k\},
              \\
              \estwV_0^\top {\q}_n,
              &
              i=0
              ,
          \end{cases}
        \end{equation}
      \end{itemize}

@@

      \begin{figure}
        \includegraphics[width=0.7\textwidth]{figures/DNN.drawio.pdf}
        \caption{Architecture of the DNN.}
      \end{figure}

@@

    \let\thefootnote\relax\footnote{
      \textit{Notations}: 
        $\mv{q}\in\R^n$: Joint position, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\estwth$: Estimated NN weights.
        $\estwth$: Estimated NN weights, $\mv{e}$: Tracking error, $\mv{\tau}_d$: Disturbance, $\mysat(\cdot)$: Saturation function.
      }

@@

    \begin{itemize}
      \item \textbf{Find} NN weights $\estwth$,
      \item That \textbf{minimize} objective function $J(\cdot)$,
        \begin{equation}\label{eq:obj}
          J(\mv{r};\estwth)
          := 
          \frac{1}{2} \mv{r}^\top \mv{r}.
        \end{equation}
        \begin{itemize}
          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is the filtered tracking error,
        \end{itemize}
      \item while satisfying the following \textbf{constraints}:
        \begin{itemize}
          \item Boundedness of the NN weights $\estwth$.
          \item Saturation of the control input $\mv{\tau}$.
        \end{itemize}
    \end{itemize}

@@

    \begin{block}{Considered Constraints}

@@

        \item \textbf{Convex control Input Saturation}: 
          \begin{itemize}
            \item Input bound constraint:
            \begin{equation}\label{eq:cstr:input_bound}
              c_{\overline{\tau}_i}(\estwth)
              :=
              \tau_i - \overline{\tau_i}
              \le 
              0
              ,
              \quad
              c_{\underline{\tau}_i}(\estwth)
              :=
              \underline{\tau_i} - \tau_i
              \le 
              0
            \end{equation}
            \item Input norm constraint:
            \begin{equation}\label{eq:cstr:input_norm}
              c_{\mv{\tau}}(\estwth)
              :=
              \norm{\mv{\tau}}^2 - \overline{\tau}^2
              \le
              0
            \end{equation}
        \end{itemize}
      \end{itemize}

    \end{block}

@@

  \textbf{Define Lagrangian Function}

  \begin{equation}\label{eq:lagrangian}
      L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
      :=
      J(\mv{r};\estwth)
      +
      \sum_{j\in\mathcal{I}} \lambda_j c_j(\estwth)
  \end{equation}

  \textbf{Dual Problem}
  \begin{itemize}
    \item The dual problem is to minimize the Lagrangian function with respect to the NN weights $\estwth$, while maximizing the Lagrange multipliers $\lambda_j$.
    \item The Lagrange multipliers $\lambda_j$ are non-negative, \ie $\lambda_j \ge 0$.
  \end{itemize}

  \begin{equation}\label{eq:dual_problem}
    \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{I}}} 
    L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
  \end{equation}

@@

    \textbf{Gradient Descent Method for $\estwth$}:
    \begin{equation}\label{eq:adaptation_law:1}
      \ddt {{\estwth}}
      =
      -\alpha 
      \ppfrac{L}{{\estwth}}
      =-\alpha 
      \left(
          \ppfrac{J}{{\estwth}}
          +
          \sum_{j\in\mathcal{I}}
          \lambda_j 
          \ppfrac{c_j}{\estwth}
      \right),
    \end{equation}

    \textbf{Gradient Ascent Method for $\lambda_j, \forall j\in\mathcal I$}:
    \begin{equation}\label{eq:adaptation_law:2}
      \ddt\lambda_j
      = 
      \beta_j
      \ppfrac{L}{\lambda_j} 
      = 
      \beta_j c_j ,
    \end{equation}

    For non-negativity of the Lagrange multipliers,
    \begin{equation}\label{eq:adaptation_law:3}
      \lambda_j
      \leftarrow
      \max(\lambda_j,0)
      .
    \end{equation}

    % \begin{subequations}
    %     \begin{align}
    %       \ddt {{\estwth}}
    %       &
    %       =
    %       -\alpha 
    %       \ppfrac{L}{{\estwth}}
    %       =-\alpha 
    %       \left(
    %           \ppfrac{J}{{\estwth}}
    %           +
    %           \sum_{j\in\mathcal{I}}
    %           \lambda_j 
    %           \ppfrac{c_j}{\estwth}
    %       \right),
    %       \\
    %       \ddt\lambda_j
    %       & 
    %       = 
    %       \beta_j
    %       \ppfrac{L}{\lambda_j} 
    %       = 
    %       \beta_j c_j ,
    %       \quad\quad\quad\quad      \      
    %       \forall j\in\mathcal I,
    %       \\
    %       \lambda_j
    %       &
    %       \leftarrow
    %       \max(\lambda_j,0)
    %     \end{align}
    % \end{subequations}

@@

    \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
      For the dynamical system described in \eqref{eq:sys}, the neuro-adaptive controller in \eqref{eq:input} with the weight adaptation laws in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the boundedness of the filtered error $\mv{r}$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption 1 and 2. This holds under the weight norm constraint \eqref{eq:cstr:weight}.
    \end{block}

@@

  Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{Ryu:2025aa}.

@@

@@

    \begin{itemize}
      \item NAC-CO denotes the proposed controller based on constrained optimization.
      \item For NAC-L2 and NAC-eMod, the stabilizing terms $-\lambda\estwth$ and $\rho\norm{\tilde{\mv{z}}}\estwth$ ensures the boundedness of the NN weights
    \end{itemize}

    \begin{table}
      \renewcommand{\arraystretch}{1.5}
      % \caption{Controller Properties.}
      \centering
      \begin{tabular}{c m{20em} c c c }
      \hline
      \textbf{Name} & \textbf{Description} & \textbf{Adaptation Law} \\
      \hline
      \hline 
        \multirow{2}{*}{NAC-CO} & Constrained Optimization-based NAC & 
      $
        \ddt\estwth = -\alpha \left(\ppfrac{L}{\estwth}+\sum_{j\in\mathcal{I}}\lambda_j\ppfrac{c_j}{\estwth}\right)
      $ 
      \\
        (proposed) & ($\beta_j$ determines $\lambda_j$ adaptation speed) &
      $
        \ddt\lambda_j = \beta_j c_j, \lambda_j \leftarrow \max(\lambda_j,0)
      $
      \\
      \hline
      \multirow{2}{*}{NAC-L2} & NAC with $L_2$-regularization & \multirow{2}{*}
      {$
        \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\lambda\estwth\right)
      $}
      \\
        & ($\lambda\in\R_{>0}$ stabilizes $\estwth$ towards origin) &
      \\
      \hline
      \multirow{2}{*}{NAC-eMod} & NAC with $\epsilon$-modification & \multirow{2}{*}
      {$
        \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\rho\norm{\tilde{\mv{z}}}\estwth\right)
      $}
      \\
      & ($\rho$ stabilizes proportionally to the error $\tilde{\mv{z}}$) &
      \\
      \hline
      \end{tabular}
      \label{table:sys:param}
    \end{table}

>>>>

% Inbuilt themes in beamer
% \documentclass[8pt, aspectratio=169, handout]{beamer}
\documentclass[8pt, aspectratio=169]{beamer}
% \setbeamertemplate{caption}[numbered]

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Define where theme files are located. ('/styles')
\usepackage{styles/fluxmacros}
\usefolder{styles}
% Use Flux theme v0.1 beta
% Available style: asphalt, blue, red, green, gray 
\usetheme[style=dding]{flux}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

% https://latexcolor.com % color list
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{awesome}{rgb}{1.0, 0.13, 0.32}
\newcommand{\ctxt}[2]{\color{#1}{#2}\color{black} }
% \newcommand{\ctxt}[2]{\color{#1}\mathbf{#2}\color{black} }

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro-Adaptive Control 
} 
\subtitle{
    \textit{IEEE European Control Conference (ECC) 2025}\\
}
\author{
  \textbf{\ctxt{airforceblue}{Myeongseok Ryu}}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
  }
\date{2025-06-25}
\institute{%
    \begin{minipage}[c]{\linewidth}
        \centering
        \inst{1}%
        Mobility Intelligence and Control Laboratory (MIC Lab) \\
        % Department of Mechanical and Robotics Engineering\\
        % Gwangju Institute of Science and Technology
        CCS Graduate School of Mobility \\
        Korea Advanced Institute of Science and Technology (KAIST)
        \and
        \inst{2}%
        AI Graduate School\\
        Gwangju Institute of Science and Technology (GIST)
  \end{minipage}
}

% \titlegraphic{assets/MIC_Lab_logo.png}
\titlegraphic{assets/MIC_Lab_logo_white.png}

% make institute font size smaller
\setbeamerfont{institute}{size=\normalsize}

@@

  \textbf{Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Neuro-adaptive control} (NAC) is a control strategy that combines \ctxt{airforceblue}{neural networks (NNs) } with \ctxt{awesome}{adaptive control } \cite{Farrell:2006aa}.
      \item Features of both \ctxt{airforceblue}{NNs } and \ctxt{awesome}{adaptive control } can be found in NAC.
    \end{itemize}
  }

@@

  \textbf{Advantages of Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item <2-> \textbf{Adaptability}: NAC adapts \ctxt{airforceblue}{NN weights }to changing environments and system dynamics.
      \item <3-> \textbf{Stability Guarantee}: The closed-loop stability is ensured using \ctxt{airforceblue}{Lyapunov stability theory}.
      \item <4-> \textbf{Online Learning Capability}: NAC adapts in \ctxt{airforceblue}{real-time } to new data with stability guarantees.
      \item <5-> \textbf{Robustness}: NAC handles \ctxt{airforceblue}{uncertainties and disturbances }effectively with adaptive control techniques.
    \end{itemize}
  }

@@

  \textbf{Existing Challenges in NAC}

  \begin{enumerate}

    \onslide<2->
    {
      \begin{columns}[T,onlytextwidth]

        \column{0.49\textwidth}

          \small{
            \item \textbf{Weight Boundedness:}

            \begin{itemize}
              \item Generally, NN weights are adapted by \ctxt{airforceblue}{gradient descent method}.
              \begin{itemize}
                \item Objective function typically consists of the control error.
              \end{itemize}
              \item Hence, the NN weights can grow \ctxt{awesome}{unbounded}, leading to instability (also known as \textit{parameter drift}).
              \item Unbounded weights can cause the NN to produce \ctxt{airforceblue}{large control inputs}, which may lead to following challenges.
            \end{itemize}
          }

          \column{0.49\textwidth}
            \centering

              \begin{figure}
                \includegraphics[width=0.7\textwidth]{figures/unbounded.drawio.pdf}
                \caption{Divergence of NN weights even with convergent control error.}
              \end{figure}
        \end{columns}
      }

      \onslide<3->
      {
        \begin{columns}[T,onlytextwidth]
          \column{0.49\textwidth}

          \small{
            \item \textbf{Unpredictable Amplitude of Control Input:}

            \begin{itemize}
              \item Typical issue of control problem in physical systems.
              \item The NN outputs are \ctxt{awesome}{unpredictable } and \ctxt{awesome}{not interpretable}.
              \item These features—unbounded NN weights and unpredictable amplitudes—can lead to \ctxt{airforceblue}{input saturation}.
            \end{itemize}
          }

          \column{0.49\textwidth}
            \centering
            \begin{figure}
              \includegraphics[width=0.8\textwidth]{figures/unpredictable.drawio.pdf}
              \caption{Unpredictable amplitude of NN outputs.}
            \end{figure}
        \end{columns}
      }

  \end{enumerate}

@@

  \begin{enumerate}

    \begin{columns}[T]

        \column{0.33\textwidth}
          \item \textbf{Projection Operator} \small{\textit{for weight boundednss}}

          \onslide<2->
          {
            \begin{itemize}
              \item Projects the NN weights onto a convex set.
              \item Ensures that the weights \ctxt{airforceblue}{remain }within a predefined bound.
            \end{itemize}

            \begin{equation}
              \estwth \leftarrow \myproj_{\overline{\theta}}(\estwth)
            \end{equation}
          }

        \column{0.33\textwidth}
          \item \textbf{$\sigma$-modification, and $\epsilon$-modification} \small{\textit{for weight boundednss}}

          \onslide<3->
          {
            \begin{itemize}
              \item Add a \ctxt{airforceblue}{stabilizing term }(\eg $ -\lambda \estwth $) to adaptation law.
              \item Construct a \ctxt{airforceblue}{invariant set }of the NN weights.
            \end{itemize}

            \begin{equation}
              \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \ctxt{awesome}{\lambda \estwth}
            \end{equation}
          }

        \column{0.33\textwidth}
          \item \textbf{Additional Control Inputs} \small{\textit{for control saturation}}

          \onslide<4->
          {
            \begin{itemize}
              \item \ctxt{airforceblue}{Conventional controllers }are used to address control input saturation. 
                    \begin{itemize}
                      \item Barrier Lyapunov function or auxiliary system-based control inputs.
                    \end{itemize}
              \item In general, \ctxt{awesome}{nominal models }are required.
            \end{itemize}
          }

@@

  \end{enumerate}

  \vspace{0.5cm}

  \begin{columns}[T]

        \onslide<2->
        {
          \centering
          \begin{figure}
            \includegraphics[width=0.8\textwidth]{figures/existing_proj.drawio.pdf}
            \caption{Projection of NN weights on a convex set.}
          \end{figure}
        }

        \onslide<3->
        {
          \centering
          \begin{figure}
            \includegraphics[width=0.8\textwidth]{figures/existing_modi.drawio.pdf}
            \caption{Adaptation result with stabilizing function (\eg $\sigma$-modification).}
          \end{figure}
        }

        \onslide<4->
        {
          \centering
          \begin{figure}
            \includegraphics[width=0.999\textwidth]{figures/existing_conv.drawio.pdf}
            \caption{Control input saturation handling with additional control inputs.}
          \end{figure}
        }

@@

  \onslide<1->
  {
    \textbf{Limitation 1: Lack of Optimality}
  }
  \begin{itemize}
    \item<2-> The existing methods do not guarantee the \ctxt{airforceblue}{optimality } of the control input.
    \item<3-> Projection operator:
    \begin{itemize}
      \item The projection operator \ctxt{awesome}{simply projects } the NN weights onto a convex set, regardless of the imposed \ctxt{airforceblue}{constraints } (\eg weight boundedness or input saturation).
      \item Moreover, if the convex set is conservatively defined, the weights may be limited to a \ctxt{awesome}{suboptimal region}.
    \end{itemize}
    \item<4-> $\sigma$- and $\epsilon$-modification:
    \begin{itemize}
      \item The stabilizing term \ctxt{awesome}{biases } the NN weights towards the origin.
      \item Therefore, the weights converge toward a \ctxt{awesome}{suboptimal point}.
    \end{itemize}
  \end{itemize}

  \onslide<1->
  {
    \textbf{Limitation 2: Disruption of Learning Process by Additional Control Inputs}
  }
  \begin{itemize}
    \item<5-> Feedback tracking error for learning is \ctxt{awesome}{disrupted } by additional control inputs.
      \begin{itemize}
        \item The feedback error \ctxt{airforceblue}{does not reflect } the error induced by the NN, directly.
        \item The additional control inputs may exceeds the \ctxt{awesome}{input saturation limits }, already.
    \end{itemize}  
  \end{itemize}

@@

  \textbf{Contribution 1: Unified Optimization Framework} 
  \onslide<2->
  {
    \begin{itemize}
      \item Trajectory tracking and constraint handling are formulated as a \ctxt{airforceblue}{unified constrained optimization } problem.
      \item The \ctxt{awesome}{conventional controllers } does not required.
      \begin{itemize}
        \item Nominal model knowledge is not required for the conventional controllers.
      \end{itemize}
    \end{itemize}
  }

  \textbf{Contribution 2: Online Learning Capability (Stability Guarantees)}
  \onslide<3->
  {
    \begin{itemize}
      \item Stability are rigorously proven using \ctxt{airforceblue}{Lyapunov stability theory}.
      \item Hence, \ctxt{airforceblue}{online learning} with \ctxt{awesome}{no prior system knowledge } is possible.
    \end{itemize}
  }

  \textbf{Contribution 3: Weight and Control Input Constraint Handling}
  \onslide<4->
  {
    \begin{itemize}
      \item Weight and control input \ctxt{awesome}{constraints } are \ctxt{airforceblue}{explicitly considered } in the optimization problem.
      \item \ctxt{airforceblue}{Any combination } of convex input constraints can be handled.
    \end{itemize}
  }

@@

    \onslide<2->
    {
      \textbf{Target Two-link Robotic Manipulator System}:
      \small{
        \begin{itemize}
          \item Control input \ctxt{awesome}{saturation function } $\mysat(\cdot)$.
          \item Desired trajectory $\mv{q}_d$ is given.
        \end{itemize}
          \begin{equation}\label{eq:sys}
            \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
            =
            \mysat(\mv{\tau})
          \end{equation}    
      }
    }

    \onslide<3->
    {
      \textbf{Control Input}:
      \small{
        \begin{itemize}
          \item NN's \ctxt{airforceblue}{output } $\mv{\Phi}$ is used as the control input.
          \item Consists of the \ctxt{awesome}{estimated NN weights } $\estwth$.
        \end{itemize}
        \begin{equation}\label{eq:input}
          \mv{\tau} := \mv{\Phi}(\mv{q}_n; \estwth)
        \end{equation}
      }
    }

    \onslide<4->
    {
      \textbf{Deep Neural Network (DNN)}:
      \small{
        \begin{itemize}
          \item $k$ layers with weights $\estwth_i:=\myvec(\estwV_i)$.
          \item Activation function: $\phi(\cdot):=tanh(\cdot)$.
          \begin{equation}\label{eq:NN}
            \mv{\Phi}(\mv{q}_n; \estwth)
            :=
            \begin{cases}
                \estwV_i^\top \act_i(\estNN_{i-1}), 
                &
                i\in\{1,\dots ,k\},
                \\
                \estwV_0^\top {\q}_n,
                &
                i=0
                ,
            \end{cases}
          \end{equation}
        \end{itemize}
      }
    }

@@

    \onslide<4->
    {
      \begin{figure}
        \includegraphics[width=0.7\textwidth]{figures/DNN.drawio.pdf}
        \caption{Architecture of the DNN.}
      \end{figure}
    }

@@

    \let\thefootnote\relax\footnote{
      \textit{Notations}: 
        $\mv{q}\in\R^n$: Joint position, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{\tau}_d$: Disturbance.
      }

@@

    \begin{itemize}
      \item \ctxt{awesome}{Find } NN weights $\estwth$,
      \item That \ctxt{airforceblue}{minimize } objective function $J(\cdot)$,
        \begin{equation}\label{eq:obj}
          J(\mv{r};\estwth)
          := 
          \frac{1}{2} \mv{r}^\top \mv{r}.
        \end{equation}
        \begin{itemize}
          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is \ctxt{awesome}{filtered tracking error},
        \end{itemize}
      \item while satisfying the following \ctxt{awesome}{constraints}:
        \begin{itemize}
          \item \ctxt{airforceblue}{Boundedness } of the NN weights $\estwth$.
          \item \ctxt{airforceblue}{Saturation } of the control input $\mv{\tau}$.
        \end{itemize}
    \end{itemize}

@@

  \onslide<2->
  {
    \begin{block}{Considered Constraints}

@@

        \item \textbf{Convex control Input Saturation}: 
          \begin{itemize}
            \item Input bound constraint \textit{for each control input}:
            \begin{equation}\label{eq:cstr:input_bound}
              c_{\overline{\tau}_i}(\estwth)
              :=
              \tau_i - \overline{\tau_i}
              \le 
              0
              ,
              \quad
              c_{\underline{\tau}_i}(\estwth)
              :=
              \underline{\tau_i} - \tau_i
              \le 
              0
            \end{equation}
            \item Input norm constraint:
            \begin{equation}\label{eq:cstr:input_norm}
              c_{\mv{\tau}}(\estwth)
              :=
              \norm{\mv{\tau}}^2 - \overline{\tau}^2
              \le
              0
            \end{equation}
        \end{itemize}
      \end{itemize}

    \end{block}
  }

@@

  \onslide<2->
  {
    \textbf{Define Lagrangian Function}

    \begin{equation}\label{eq:lagrangian}
        L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
        :=
        J(\mv{r};\estwth)
        +
        \sum_{j\in\mathcal{I}} \lambda_j c_j(\estwth)
    \end{equation}
  }

  \onslide<3->
  {
    \textbf{Dual Problem}
    \begin{itemize}
      \item The dual problem is to \ctxt{airforceblue}{minimize } the Lagrangian function with respect to the \ctxt{airforceblue}{NN weights } $\estwth$, while \ctxt{awesome}{maximizing } with respect to the \ctxt{awesome}{Lagrange multipliers } $\lambda_j$.
      \item The Lagrange multipliers $\lambda_j$ are non-negative, \ie $\lambda_j \ge 0$.
    \end{itemize}

    \begin{equation}\label{eq:dual_problem}
      \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{I}}} 
      L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
    \end{equation}
  }

@@

    \onslide<2->
    {
      \textbf{Gradient \ctxt{airforceblue}{Descent } Method for weights $\estwth$}:
      \begin{equation}\label{eq:adaptation_law:1}
        \ddt {{\estwth}}
        =
        -\alpha 
        \ppfrac{L}{{\estwth}}
        =-\alpha 
        \left(
            \ppfrac{J}{{\estwth}}
            +
            \sum_{j\in\mathcal{I}}
            \lambda_j 
            \ppfrac{c_j}{\estwth}
        \right),
      \end{equation}
    }

    \onslide<3->
    {
      \textbf{Gradient \ctxt{awesome}{Ascent } Method for Lagrange multipliers $\lambda_j, \forall j\in\mathcal I$}:
      \begin{equation}\label{eq:adaptation_law:2}
        \ddt\lambda_j
        = 
        \beta_j
        \ppfrac{L}{\lambda_j} 
        = 
        \beta_j c_j ,
      \end{equation}
    }

    \onslide<4->
    {
      For non-negativity of the Lagrange multipliers,
      \begin{equation}\label{eq:adaptation_law:3}
        \lambda_j
        \leftarrow
        \max(\lambda_j,0)
        .
      \end{equation}
    }

@@

    \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
      For the \ctxt{airforceblue}{dynamical system } described in \eqref{eq:sys}, the \ctxt{awesome}{neuro-adaptive controller } in \eqref{eq:input} with the \ctxt{airforceblue}{weight adaptation laws } in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the \ctxt{airforceblue}{boundedness } of the \ctxt{awesome}{filtered error } $\mv{r}$ and the \ctxt{awesome}{weight estimate } $\estwth$, under the control input constraints satisfying Assumption 1 and 2. This holds under the \ctxt{awesome}{weight norm constraint } \eqref{eq:cstr:weight}.
    \end{block}

@@

  Proof of Theorem 1 is \textbf{omitted } due to space limitations. The detailed proof can be found in \cite{Ryu:2025aa}.

@@

\begin{frame}{\insertsubsectionhead}{Controllers Setting}

  \begin{itemize}
    \item Only \ctxt{awesome}{weight norm constraint } is considered in this presentation (for \textbf{ECC}).
    \item Input saturation constraints are not considered.
  \end{itemize}

  \centering
  \begin{figure}
    \includegraphics[width=0.8\textwidth]{figures/Controller.drawio.pdf}
    \caption{Architecture of the controllers.}
  \end{figure}

@@

    \begin{itemize}
      \item NAC-CO denotes the proposed controller based on \ctxt{airforceblue}{constrained optimization }.
      \item For NAC-L2 and NAC-eMod, the \ctxt{awesome}{stabilizing terms } $-\lambda\estwth$ and $\rho\norm{\mv{r}}\estwth$ ensures the weights boundedness, respectively.
    \end{itemize}

    \begin{table}
      \renewcommand{\arraystretch}{1.5}
      % \caption{Controller Properties.}
      \centering
      \begin{tabular}{c m{20em} c c c }
      \hline
      \textbf{Name} & \textbf{Description} & \textbf{Adaptation Law} \\
      \hline
      \hline 
        \multirow{2}{*}{NAC-L2} & NAC with $L_2$-regularization \tiny{(equal to $\sigma$-modification)} & \multirow{2}{*}
        {$
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\lambda}\estwth\right)
        $}
        \\
          & ($\ctxt{awesome}{\lambda}$ stabilizes $\estwth$ towards origin) &
        \\
      \hline
        \multirow{2}{*}{NAC-eMod} & NAC with $\epsilon$-modification & \multirow{2}{*}
        {$
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\rho}\norm{\tilde{\mv{z}}}\estwth\right)
        $}
        \\
        & ($\ctxt{awesome}{\rho}$ stabilizes proportionally to filtered error $\mv{r}$) &
        \\
      \hline
        \multirow{2}{*}{NAC-CO} & Constrained Optimization-based NAC & 
        $
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\sum_{j\in\mathcal{I}}\lambda_j\ppfrac{c_j}{\estwth}\right)
        $ 
        \\
          (proposed) & ($\ctxt{awesome}{\beta_j}$ determines $\lambda_j$ adaptation speed) &
        $
          \ddt\lambda_j = \ctxt{awesome}{\beta_j} c_j$, and $\lambda_j \leftarrow \max(\lambda_j,0)
        $
        \\
      \hline
      \end{tabular}
      \label{table:sys:param}
    \end{table}
